---
title: "Untitled"
output: html_document
date: "2024-07-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we install al the necessary libraries:

```{r}
library(tidyverse)
library(DESeq2)
library(knitr)
library(rtracklayer)
library(RColorBrewer)
library(pheatmap)
```


# D27-35 VS D12-13

## Start of the analysis.


```{r}
# Import rawcounts generated from Salmon after the previous RNA-seq analysis
library(readxl)
rawcounts <- read_excel("C:/Users/HR Sergio/Desktop/Postdoc/Cerebellum project/RNA-seq output/salmon/Table_Rawcounts_.xlsx")
# Change names of the columns
colnames(rawcounts) <- c("gene_id", "d12_s2","d12_s3","d13_s1", "d13_s2", "d27_s1", "d27_s2", "d35_s1", "d35_s2","d35_s3")
# Be sure all raw counts data is an integer
rawcounts$d12_s2 <- as.integer(as.character(rawcounts$d12_s2))
rawcounts$d12_s3 <- as.integer(as.character(rawcounts$d12_s3))
rawcounts$d13_s1 <- as.integer(as.character(rawcounts$d13_s1))
rawcounts$d13_s2 <- as.integer(as.character(rawcounts$d13_s2))
rawcounts$d27_s1 <- as.integer(as.character(rawcounts$d27_s1))
rawcounts$d27_s2 <- as.integer(as.character(rawcounts$d27_s2))
rawcounts$d35_s1 <- as.integer(as.character(rawcounts$d35_s1))
rawcounts$d35_s2 <- as.integer(as.character(rawcounts$d35_s2))
rawcounts$d35_s3 <- as.integer(as.character(rawcounts$d35_s3))
# Convert the column with the gene id in rows to proceed with the further analysis
rawcounts %>% as.data.frame() %>% 
  column_to_rownames(var ="gene_id") -> rawcounts
```

## Creation of metadata

Creation of vector containing metadata for the samples

```{r}
# In this case we generate only one vector since the only condition we need to take into account is the age of the CRBOs
age <- c("d12-13","d12-13","d12-13", "d12-13", "d27-35", "d27-35", "d27-35", "d27-35","d27-35")
```

Combine the vectors in a data frame and then add the exact names of the samples:

```{r}
info.data <- data.frame(age)
rownames(info.data) <- c("d12_s2","d12_s3","d13_s1", "d13_s2", "d27_s1", "d27_s2", "d35_s1", "d35_s2","d35_s3")
info.data
```

## Check sample order

Row names in the metadata data frame and column names in the rawcounts data frame should be the same

```{r}
# We need to get a TRUE message if we want to continue using the data. 
all(rownames(info.data) == colnames(rawcounts))
```

## Create the DESeq2 object

```{r}
dds <- DESeqDataSetFromMatrix(countData = rawcounts,
                              colData = info.data,
                              design = ~ age)
dds
# Now we select the levels of the comparison. Here only 2 levels since we will put together 12 and 13 samples and 27 and 35 samples. Control condition will be 12-13 days samples and that is the reason why they go first
dds$age <- factor(dds$age, levels = c("d12-13", "d27-35"))
```

## Unsupervised clustering analysis: log transformation 

VST means variance stabilizing transformations and produce trnasformed data on the log2 scale which has been normalized with respect to library size. The point of this is to remove the dependence of the variance of the mean, particularly the high variance of the logarithm of count data when the mean is low. The argument blind should be equal to TRUE when is used in order to compare samples in a manner wholly unbiased by the information about experimental groups. However, blind dispersion estimation is not the appropiate choice if one expects that many of the majority of genes will have large differences in counts which are explainable by the experimental design

```{r}
vst <- vst(dds, blind = TRUE)
```

## Heatmap of the sample-to-sample correlation

```{r}
# the assay function extract the vst matrix from the vst object
vst_matrix <- assay(vst) 
# we compute pairwise correlation values
vst_cor <- cor(vst_matrix)
# we generate a heatmap in which we can see the correlation values. Similar to sample to samples distances heatmap that will be done afterwards. This is not included in the memory
pheatmap(vst_cor, cluster_cols = TRUE, show_rownames = TRUE, show_colnames = FALSE, cluster_rows = TRUE, annotation_col = info.data)
```

## Heatmap of the sample-to-sample distances. Extracting transformed values

For the sample clustering, we apply the dist function to the transposase of the transformed count matrix to get sample-to-sample distances. A heatmap of this distance matrix gives us an overview over SIMILARITIES and DISSIMILARITIES between samples

```{r}
# vst transformation as explained above
vsd <- vst(dds, blind=FALSE)
# dist function to the transposase of the transformed count matrix to get sample-to-sample distances instead of correlation values as before
sampleDists <- dist(t(assay(vsd)))
# generation of a matrix with the sample distance data
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$age)
colnames(sampleDistMatrix) <- NULL
# generation of a heatmap with the sample to samples distance matrix
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix, cluster_rows = TRUE, cluster_cols = TRUE,col=colors, show_rownames = TRUE)
```

## PCA

This command will plot automatically PC1 and PC2: The objec has to be a DESeqTransform object, with data in assay(x), produced by either rlog or vst.

```{r}
# we produce the PCA plot using the vst object and the age vector of metadata
plotPCA(vst, intgroup = c("age"))
```


## Differentail expression analysis

The standard differential expression analysis steps are wrapped into a single function, DESeq:

```{r}
dds <- DESeq(dds)
```

The function results() extracts a results table from a DESeq analysis giving base means across samples, log2 fold changes, standard errors, test statistics, pvalues and adj p values.
The results() function automatically performs independent filtering based on the mean of normalized counts for each gene, optimizing the number of genes which will have an adjusted p value below a given FDR cutoff, in this case 0.05. 
So, basically, the new matrix result will be the same as dds but after filtering and optimizing the genes which will have and adj p value below 0.05

```{r}
result <- results(dds, alpha = 0.05)
#The results table, when printed, will provide the information about the comparison, e.g. "log2 fold change:day27-35 vs day 12-13". If results is run without specifying contrast or name, it will return the comparison of the last level of the last variable in the design formula over the first level of this variable. For example, for a simple two-group comparison, this would return the log2 fold changes of the second group (day 27-35) over the first group (the control day12-13). 
```

How many adjusted p-values were less than 0.05?

```{r}
sum(result$padj < 0.05, na.rm = TRUE)
```


## Log fold change shrinkage for visualization and ranking

Shrinkage of effect size (LFC estimates) is useful for visualization and ranking of genes. We pass the dds object to the function lfcShrink. Below we specify to use the "apeglm" method to effect size shrinkage.
We provide the dds object and the name or number of the coefficient we want to shrink, which we know using the function resultsNames()

```{r}
#if (!requireNamespace("BiocManager", quietly = TRUE))
    #install.packages("BiocManager")

#BiocManager::install("apeglm")
```

```{r}
#lfcShrink would be doing the same as results() function but more strictly an shrinkage the effect size
ape <- lfcShrink(dds = dds, coef = 2, type = "apeglm")
sum(ape$padj < 0.05, na.rm = TRUE)
```

## MAplot

In DESeq2, the plotMA function shows the log2 fold changes attributable to a given variable over the mean of normalized counts for all the samples in the DESeqDataSet

```{r}
# without shrinkage. Not used in the memory
DESeq2::plotMA(result, ylim=c(-10,10), cex=.6)
```

It is more useful to visualize the MAplot for the shrunken log2 fold changes, which remove the noise associated with log2 fold changes from low count genes without requiring arbitrary filtering thresholds:

```{r}
# with shrinkage
DESeq2::plotMA(ape, ylim=c(-10,10), cex=.6)
```

## Annotation of the results

For the annotation we need to use the same file that was used for the mapping in STAR step. In this case, we already got the mapped counts, so we can use the previous table that we generated. We will use the shrinkaged file for further analysis

```{r}
#We will need to make every result a data frame. 
ape_df <- data.frame(ape)
```

```{r}
# we import the human genome that was used previously in the mapping step
gtf <- import("C:/Users/HR Sergio/Desktop/Homo_sapiens.GRCh38.103.gtf")
# we generate a data frame from the gtf object
annotation_genes <- data.frame(gtf)
# we take only the columns of interest. In this case, the gene name and the gene id to generate a gene_names data frame that will be used later 
gene_names <- annotation_genes[,c(10,12)]
colnames(gene_names) <- c("Gene","GeneName")
```


```{r}
##With the following command we will call to the first column GeneName
ape_df <- ape_df %>% 
  rownames_to_column(var = "Gene")

##With this one we will join both data frames by GeneName and use the distincit() function to remove duplicates
ape_df <- left_join(ape_df,
          gene_names,
          by = "Gene") %>% 
  distinct(Gene, .keep_all = TRUE)
```

To save it:

```{r}
write_tsv(as.data.frame(ape_df),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d27-35vsd12-13/CRB_d27-35vsd12-13.tsv")
```

## Arrange DE genes according to their adjusted p-value

We are going to establish a threshold of an adjusted p-value lower than 0.05

for the shrinkaged file:

```{r}
subset(ape_df, padj < 0.05) -> sig_genes_d35_vs_d1213
# we export it in tsv format
write_tsv(as.data.frame(sig_genes_d35_vs_d1213),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d27-35vsd12-13/sig_genes_CRB_d27-35vsd12-13.tsv")
```


## RPKM calculation

We are going to extract the rawcounts from the dds object that has already a filtering step. 

```{r}
rawcount_2 <- counts(dds)
```

```{r}
# we take only the columns of interest from the human genome data frame that we generated before. In this case, the ensemble gene id and the gene length that we need to be able to generate rpkm
gene_length <- annotation_genes[,c(4,10)]
colnames(gene_length) <- c("Length","Gene")
#remove duplicates in rows since sometimes there are more than one ensemble id for the same gene name (based on different transcripts)
gene_length <- gene_length[!duplicated(gene_length[c('Gene')]), ]
```

```{r}
#After extraction of the gene length, we transform the results from bp to kb
gene_length <- gene_length %>% 
    mutate(length_kb = Length/1000)
gene_length
  
# scaling factor. Here we are obtaining the reads per million for each individual sample. It is row wise. This is indicated using the number 2 in the function. 
  scale_factor <- apply(rawcount_2,
    2, function(x) sum(x))/1000000
  
# normalize to library size using the scale factor of each sample. Basically, what we are doing here is to divide the raw counts of each gene by the scale factor of each sample. That means, the raw counts of the first gene in the first sample divided by the scale factor in the 8 different samples, and we get the norm counts of each gene in each sample
norm_counts <- rawcount_2 %>%  
    sweep(., 2, scale_factor, "/")

# rpkm: To calculate it, first of all we join the two tables: rawcount_2 and gene_length
rawcount_2 %>% as.data.frame() %>% 
  rownames_to_column(var = "Gene") -> rawcount_2

##With this one we will join both data frames by Gene
all_info <- left_join(rawcount_2,
          gene_length,
          by = "Gene") %>% 
  distinct(Gene, .keep_all = TRUE)

#Now, we divide the normalized counts of each gene by the length of the gene in kb   
rpkm <- norm_counts %>% 
  sweep(., 1, all_info$length_kb, "/")
rpkm %>% as.data.frame() %>% 
  rownames_to_column(var = "Gene") -> rpkm
#Now we use the previous data frame called gene_names to map it with the ensembl ones
rpkm_final <- left_join(gene_names,
          rpkm,
          by = "Gene") %>% 
  distinct(Gene, .keep_all = TRUE)
```

To save it:

```{r}
write_tsv(as.data.frame(rpkm_final),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/rpkm-final.tsv")
```


## RPKM Heatmap of Cerebellum markers

Once we generated rpkm for each sample, then we performed the average for each CONDITION (hESC-day0,2 weeks-day12-13, 4 weeks-day27, 5 weeks-day35) and then we import that file to be used for the next heatmap:

```{r}
# Import the average rpkm for each condition
library(readxl)
RPKM <- read_excel("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/rpkm_average.xlsx")
# Remove duplicates
RPKM <- RPKM[!duplicated(RPKM[c('Gene')]), ]
```


```{r}
# Now we select a variety of genes that we know are markers for different cell types observed in the cerebellum, to see how it is their time-dependent gene expression
library(dplyr)
rpkm_df <-as.data.frame(filter(RPKM, Gene == "SOX1" | Gene == "SOX2" | Gene == "GBX2" | Gene == "PAX2" | Gene == "EN2" | Gene == "MAP2" | Gene == "TUBB3" | Gene == "RBFOX3" | Gene == "NCAM1" | Gene == "NCAM2" | Gene == "NEUROD1" | Gene == "OTX1" | Gene == "OTX2" | Gene == "PAX6" | Gene == "LMX1A" | Gene == "ATOH1" | Gene == "PTF1A" | Gene == "GSX1" | Gene == "KIRREL2" | Gene == "LHX2" | Gene == "TBR1" | Gene == "BARHL1" | Gene == "CEP131" | Gene == "KIF3A" | Gene == "ARL13B" | Gene == "IFT88" | Gene == "PVALB" | Gene == "EOMES" | Gene == "OLIG2" | Gene == "SKOR2" | Gene == "CALB1" | Gene == "CALB2" | Gene == "GAD1" | Gene == "LHX5" | Gene == "GRID2" | Gene == "GAD2" | Gene == "SHH" | Gene == "SMO" | Gene == "PTCH1" | Gene == "GLI1" | Gene == "CCND1" | Gene == "MYCN" | Gene == "OLIG1" | Gene == "SOX10"| Gene == "PDGFRA" | Gene == "CSPG4"| Gene == "GFAP" | Gene == "APOE"| Gene == "AQP4"))
# This part is to keep the same order given above
sub_anno <- structure(list(seq_share = c("A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A","A")), .Names = "state", row.names = c("SOX1","SOX2","GBX2","PAX2","EN2","MAP2","TUBB3","RBFOX3","NCAM1","NCAM2","NEUROD1","OTX1","OTX2","PAX6","LMX1A","ATOH1","PTF1A","GSX1","KIRREL2","LHX2","TBR1","BARHL1","CEP131","KIF3A","ARL13B","IFT88","PVALB","EOMES","OLIG2","SKOR2","CALB1","CALB2","GAD1","LHX5","GRID2","GAD2","SHH","SMO","PTCH1","GLI1","CCND1","MYCN","OLIG1","SOX10","PDGFRA","CSPG4","GFAP","APOE","AQP4"), class = "data.frame")
rpkm_df <- tibble::column_to_rownames(rpkm_df, "Gene")
# Here we say that we want to keep the same order as mentioned above
rpkm_df_ordered <- rpkm_df[rownames(sub_anno), ]
# We generate the heatmap
a <- pheatmap(rpkm_df_ordered,  scale= "row", cluster_cols = FALSE, show_rownames = TRUE, show_colnames = FALSE, cluster_rows = FALSE, fontsize_row = 5)
```




# D35 VS D12-13

## Start of the analysis.

```{r}
library(readxl)
rawcounts <- read_excel("C:/Users/HR Sergio/Desktop/Postdoc/Cerebellum project/RNA-seq output/salmon/Table_Rawcounts_.xlsx")
colnames(rawcounts) <- c("gene_id", "d12_s2","d12_s3","d13_s1", "d13_s2", "d27_s1", "d27_s2", "d35_s1", "d35_s2","d35_s3")
rawcounts$d12_s2 <- as.integer(as.character(rawcounts$d12_s2))
rawcounts$d12_s3 <- as.integer(as.character(rawcounts$d12_s3))
rawcounts$d13_s1 <- as.integer(as.character(rawcounts$d13_s1))
rawcounts$d13_s2 <- as.integer(as.character(rawcounts$d13_s2))
rawcounts$d27_s1 <- as.integer(as.character(rawcounts$d27_s1))
rawcounts$d27_s2 <- as.integer(as.character(rawcounts$d27_s2))
rawcounts$d35_s1 <- as.integer(as.character(rawcounts$d35_s1))
rawcounts$d35_s2 <- as.integer(as.character(rawcounts$d35_s2))
rawcounts$d35_s3 <- as.integer(as.character(rawcounts$d35_s3))
rawcounts %>% as.data.frame() %>% 
  column_to_rownames(var ="gene_id") -> rawcounts
#We remove d27 samples for the further analysis
rawcounts <- rawcounts[,-c(5,6)]
```

## Creation of metadata

```{r}
age <- c("d12-13","d12-13","d12-13", "d12-13", "d35", "d35","d35")
info.data <- data.frame(age)
info.data
rownames(info.data) <- c("d12_s2","d12_s3","d13_s1", "d13_s2", "d35_s1", "d35_s2","d35_s3")
info.data
```

## Check sample order

```{r}
all(rownames(info.data) == colnames(rawcounts))
```

## Create the DESeq2 object

```{r}
dds <- DESeqDataSetFromMatrix(countData = rawcounts,
                              colData = info.data,
                              design = ~ age)
dds
dds$age <- factor(dds$age, levels = c("d12-13", "d35"))
```


## Unsupervised clustering analysis: log transformation 

```{r}
vst <- vst(dds, blind = TRUE)
```

## Heatmap of the sample-to-sample correlation

```{r}
vst_matrix <- assay(vst) 
dim(vst_matrix)
vst_cor <- cor(vst_matrix)
pheatmap(vst_cor, cluster_cols = TRUE, show_rownames = TRUE, show_colnames = FALSE, cluster_rows = TRUE, annotation_col = info.data)
```

## Heatmap of the sample-to-sample distances. Extracting transformed values


```{r}
vsd <- vst(dds, blind=FALSE)
sampleDists <- dist(t(assay(vsd)))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$genotype)
colnames(sampleDistMatrix) <- NULL
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix, cluster_rows = TRUE, cluster_cols = TRUE,col=colors)
```

## PCA

```{r}
plotPCA(vst, intgroup = c("age"))
```


## Differentail expression analysis


```{r}
dds <- DESeq(dds)
result <- results(dds, alpha = 0.05)
summary(result)
sum(result$padj < 0.05, na.rm = TRUE)
```

## Log fold change shrinkage for visualization and ranking

```{r}
ape <- lfcShrink(dds = dds, coef = 2, type = "apeglm")
sum(ape$padj < 0.05, na.rm = TRUE)
```
## MAplot

```{r}
DESeq2::plotMA(result, ylim=c(-10,10), cex=.6)
```

```{r}
plotMA(ape, ylim=c(-10,10), cex=.6)
```

## Annotation of the results

```{r}
ape_df <- data.frame(ape)
gtf <- import("C:/Users/HR Sergio/Desktop/Homo_sapiens.GRCh38.103.gtf")
annotation_genes <- data.frame(gtf)
gene_names <- annotation_genes[,c(10,12)]
colnames(gene_names) <- c("Gene","GeneName")
```

```{r}
ape_df <- ape_df %>% 
  rownames_to_column(var = "Gene")
ape_df <- left_join(ape_df,
          gene_names,
          by = "Gene") %>% 
  distinct(Gene, .keep_all = TRUE)
```


```{r}
write_tsv(as.data.frame(ape_df),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/CRB_d35vsd12-13.tsv")
```

## Arrange DE genes according to their adjusted p-value

```{r}
subset(ape_df, padj < 0.05) -> sig_genes_d35_vs_d1213
write_tsv(as.data.frame(sig_genes_d35_vs_d1213),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/sig_genes_CRB_d35vsd12-13.tsv")
```

Here we received new samples from hESC RNA sequencing that were considered as day 0

## BARPLOTS FROM ENRICHMENT FILES 

### UPREGULATION

#### BioPlanet enrichr

```{r}
# First we need to install and call the library readxl in order to import the file downloaded from ENRICHR
library(readxl)
# Now we import it putting the path where they are located in your computer
BioPlanet <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/UPREGULATION/BioPlanet_2019_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(BioPlanet$`Adjusted P-value`) -> BioPlanet$`Adjusted P-value`
as.numeric(BioPlanet$`P-value`) -> BioPlanet$`P-value`
# We select only the columns we are interested on
BioPlanet_FDR <- BioPlanet[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
BioPlanet_FDR_top10 <- BioPlanet_FDR[c(1:10),]
#And we change the name of the columns
colnames(BioPlanet_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#To make the plot, we need the function ggplot from the tidyverse library
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is grey
BioPlanet_plot <- ggplot(BioPlanet_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#999999") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 BioPlanet pathway") +
    ylab("-log10(pval)")
BioPlanet_plot <- BioPlanet_plot + theme(text = element_text(size = 5))
BioPlanet_plot
```


#### KEGG enrichr

```{r}
# First we need to install and call the library readxl in order to import the file from the computer
library(readxl)
# Now we import it putting the path where they are located in your computer
KEGG <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/UPREGULATION/KEGG_2021_Human_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(KEGG$`Adjusted P-value`) -> KEGG$`Adjusted P-value`
as.numeric(KEGG$`P-value`) -> KEGG$`P-value
# We select only the columns we are interested on
KEGG_FDR <- KEGG[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
KEGG_FDR_top10 <- KEGG_FDR[c(1:10),]
#And we change the name of the columns
colnames(KEGG_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is brown
KEGG_plot <- ggplot(KEGG_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="brown3") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 KEGG pathway") +
    ylab("-log10(pval)")
KEGG_plot <- KEGG_plot + theme(text = element_text(size = 5))
KEGG_plot
```

#### GO CELLULAR COMPONENT Enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
GO_Cellular_Component <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/UPREGULATION/GO_Cellular_Component_2023_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(GO_Cellular_Component$`Adjusted P-value`) -> GO_Cellular_Component$`Adjusted P-value`
as.numeric(GO_Cellular_Component$`P-value`) -> GO_Cellular_Component$`P-value`
# We select only the columns we are interested on
GO_Cellular_Component_FDR <- GO_Cellular_Component[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
GO_Cellular_Component_FDR_top10 <- GO_Cellular_Component_FDR[c(1:10),]
#And we change the name of the columns
colnames(GO_Cellular_Component_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is yellow
GO_Cellular_Component_plot <- ggplot(GO_Cellular_Component_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#E69F00") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 GO Celluar Component") +
    ylab("-log10(pval)")
GO_Cellular_Component_plot <- GO_Cellular_Component_plot + theme(text = element_text(size = 5))
GO_Cellular_Component_plot
```

#### Ingenuity Pathway Analysis 

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
IPA_UP <- read_excel("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/IPA/upregulation.xlsx")
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(IPA_UP$LOGP) -> IPA_UP$LOGP
# We confirm that they are numeric class
class(IPA_UP$LOGP) 
# We select only the columns we are interested on
IPA_UP_FDR <- IPA_UP[,-c(3,4,5)]
# And now only the first 20 rows/pathways
IPA_UP_FDR_top20 <- IPA_UP_FDR[c(1:20),]
#And we change the name of the columns
colnames(IPA_UP_FDR_top20) <- c("Term", "LOGP")
#And now we make the plot using -log10 pval for the representation of the top5 entiched pathways. The number in the fill part represent a color, in this case is blue
IPA_UP_plot <- ggplot(IPA_UP_FDR_top20, aes(x=reorder(Term, LOGP), y=LOGP)) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="blue") +
    coord_flip() +
    theme_classic() +
    xlab("Top 20 IPA") +
    ylab("-log10(pval)")
IPA_UP_plot <- IPA_UP_plot + theme(text = element_text(size = 5))
IPA_UP_plot
```

### DOWNREGULATION

#### BioPlanet enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
BioPlanet <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/DOWNREGULATION/BioPlanet_2019_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(BioPlanet$`Adjusted P-value`) -> BioPlanet$`Adjusted P-value`
as.numeric(BioPlanet$`P-value`) -> BioPlanet$`P-value`
# We confirm that they are numeric class
class(BioPlanet$Adjusted.P.value) 
# We select only the columns we are interested on
BioPlanet_FDR <- BioPlanet[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
BioPlanet_FDR_top10 <- BioPlanet_FDR[c(1:10),]
#And we change the name of the columns
colnames(BioPlanet_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is grey
BioPlanet_plot <- ggplot(BioPlanet_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#999999") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 BioPlanet pathway") +
    ylab("-log10(pval)")
BioPlanet_plot <- BioPlanet_plot + theme(text = element_text(size = 5))
BioPlanet_plot
```


#### KEGG enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
KEGG <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/DOWNREGULATION/KEGG_2021_Human_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(KEGG$`Adjusted P-value`) -> KEGG$`Adjusted P-value`
as.numeric(KEGG$`P-value`) -> KEGG$`P-value`
# We select only the columns we are interested on
KEGG_FDR <- KEGG[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
KEGG_FDR_top10 <- KEGG_FDR[c(1:10),]
#And we change the name of the columns
colnames(KEGG_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is brown
KEGG_plot <- ggplot(KEGG_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="brown3") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 KEGG pathway") +
    ylab("-log10(pval)")
KEGG_plot <- KEGG_plot + theme(text = element_text(size = 5))
KEGG_plot
```

#### GO CELLULAR COMPONENT

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
GO_Cellular_Component <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/ENRICHR/DOWNREGULATION/GO_Cellular_Component_2023_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(GO_Cellular_Component$`Adjusted P-value`) -> GO_Cellular_Component$`Adjusted P-value`
as.numeric(GO_Cellular_Component$`P-value`) -> GO_Cellular_Component$`P-value`
# We select only the columns we are interested on
GO_Cellular_Component_FDR <- GO_Cellular_Component[,c(1,3,4,9)]
# And now only the first 5 rows/pathways
GO_Cellular_Component_FDR_top10 <- GO_Cellular_Component_FDR[c(1:10),]
#And we change the name of the columns
colnames(GO_Cellular_Component_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
library(tidyverse)
#And now we make the plot using -log10 pval for the representation of the top5 entiched pathways. The number in the fill part represent a color, in this case is yellow
GO_Cellular_Component_plot <- ggplot(GO_Cellular_Component_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#E69F00") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 GO Cellular components") +
    ylab("-log10(pval)")
GO_Cellular_Component_plot <- GO_Cellular_Component_plot + theme(text = element_text(size = 5))
GO_Cellular_Component_plot
```

#### Ingenuity Pathway Analysis 

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
IPA_UP <- read_excel("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd12-13/IPA/downregulation.xlsx")
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(IPA_UP$LOGP) -> IPA_UP$LOGP
# We confirm that they are numeric class
class(IPA_UP$LOGP) 
# We select only the columns we are interested on
IPA_UP_FDR <- IPA_UP[,-c(3,4,5)]
# And now only the first 20 rows/pathways
IPA_UP_FDR_top20 <- IPA_UP_FDR[c(1:20),]
#And we change the name of the columns
colnames(IPA_UP_FDR_top20) <- c("Term", "LOGP")
#And now we make the plot using -log10 pval for the representation of the top5 entiched pathways. The number in the fill part represent a color, in this case is BLUE
IPA_UP_plot <- ggplot(IPA_UP_FDR_top20, aes(x=reorder(Term, LOGP), y=LOGP)) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="blue") +
    coord_flip() +
    theme_classic() +
    xlab("Top 20 IPA") +
    ylab("-log10(pval)")
IPA_UP_plot <- IPA_UP_plot + theme(text = element_text(size = 5))
IPA_UP_plot
```

# D35 vs D0

## Start of the analysis.

```{r}
# Import rawcounts generated from Salmon after the previous RNA-seq analysis
library(readxl)
rawcounts_2 <- read_excel("C:/Users/HR Sergio/Desktop/Postdoc/Cerebellum project/RNA-seq output/salmon/Table_Rawcounts_.xlsx")
rawcounts_1 <- read_excel("C:/Users/HR Sergio/Desktop/Postdoc/Cerebellum project/RNA-seq output NEW/Table-Rawcounts.xlsx")
rawcounts <- left_join(rawcounts_1,
          rawcounts_2,
          by = "gene_id") %>% 
  distinct(gene_id, .keep_all = TRUE)
#There are some columns that are samples from another project that we don't need here. They are columns 5 and 6
rawcounts <- rawcounts[,c(1,2,3,4,7,8,9,10,11,12,13,14,15)]
# Change names of the columns
colnames(rawcounts) <- c("gene_id", "d0_s2_G","d0_s2_I","d0_s3_G", "d12_s2","d12_s3","d13_s1", "d13_s2", "d27_s1", "d27_s2", "d35_s1", "d35_s2","d35_s3")
# Be sure all raw counts data is an integer
rawcounts$d0_s2_G <- as.integer(as.character(rawcounts$d0_s2_G))
rawcounts$d0_s2_I <- as.integer(as.character(rawcounts$d0_s2_I))
rawcounts$d0_s3_G <- as.integer(as.character(rawcounts$d0_s3_G))
rawcounts$d12_s2 <- as.integer(as.character(rawcounts$d12_s2))
rawcounts$d12_s3 <- as.integer(as.character(rawcounts$d12_s3))
rawcounts$d13_s1 <- as.integer(as.character(rawcounts$d13_s1))
rawcounts$d13_s2 <- as.integer(as.character(rawcounts$d13_s2))
rawcounts$d27_s1 <- as.integer(as.character(rawcounts$d27_s1))
rawcounts$d27_s2 <- as.integer(as.character(rawcounts$d27_s2))
rawcounts$d35_s1 <- as.integer(as.character(rawcounts$d35_s1))
rawcounts$d35_s2 <- as.integer(as.character(rawcounts$d35_s2))
rawcounts$d35_s3 <- as.integer(as.character(rawcounts$d35_s3))
# Convert the column with the gene id in rows to proceed with the further analysis
rawcounts %>% as.data.frame() %>% 
  column_to_rownames(var ="gene_id") -> rawcounts
```

## Creation of metadata

```{r}
age <- c("d0","d0","d0", "d12-13","d12-13","d12-13", "d12-13","d27","d27", "d35", "d35", "d35")
info.data <- data.frame(age)
info.data
rownames(info.data) <- c("d0_s2_G","d0_s2_I","d0_s3_G", "d12_s2","d12_s3","d13_s1", "d13_s2", "d27_s1", "d27_s2", "d35_s1", "d35_s2","d35_s3")
info.data
```

## Check sample order

```{r}
all(rownames(info.data) == colnames(rawcounts))
```

## Create the DESeq2 object

```{r}
dds <- DESeqDataSetFromMatrix(countData = rawcounts,
                              colData = info.data,
                              design = ~ age)
dds
dds$age <- factor(dds$age, levels = c("d0","d12-13", "d27","d35"))
```


## Unsupervised clustering analysis: log transformation 

```{r}
vst <- vst(dds, blind = TRUE)
```

## Heatmap of the sample-to-sample correlation

```{r}
vst_matrix <- assay(vst) 
dim(vst_matrix)
vst_cor <- cor(vst_matrix)
pheatmap(vst_cor, cluster_cols = TRUE, show_rownames = TRUE, show_colnames = FALSE, cluster_rows = TRUE, annotation_col = info.data)
```

## Heatmap of the sample-to-sample distances. Extracting transformed values


```{r}
vsd <- vst(dds, blind=FALSE)
sampleDists <- dist(t(assay(vsd)))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$genotype)
colnames(sampleDistMatrix) <- NULL
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
pheatmap(sampleDistMatrix, cluster_rows = TRUE, cluster_cols = TRUE,col=colors)
```

## PCA

Please, check RUV+Deseq2 trial file

## Differentail expression analysis


```{r}
dds <- DESeq(dds)
```

## Log fold change shrinkage for visualization and ranking

```{r}
# the following function is to know the order of the different comparisons, in order to put it later in the coef functions
resultsNames(dds)
# Here we are insterested in the comparison d35 vs d0, so the position 4
ape <- lfcShrink(dds = dds, coef = 4, type = "apeglm")
sum(ape$padj < 0.05, na.rm = TRUE)
```
## MAplot

```{r}
DESeq2::plotMA(ape, ylim=c(-10,10), cex=.6)
```

## Annotation of the results

```{r}
ape_df <- data.frame(ape)
gtf <- import("C:/Users/HR Sergio/Desktop/Homo_sapiens.GRCh38.103.gtf")
annotation_genes <- data.frame(gtf)
gene_names <- annotation_genes[,c(10,12)]
colnames(gene_names) <- c("Gene","GeneName")
```

```{r}
ape_df <- ape_df %>% 
  rownames_to_column(var = "Gene")
ape_df <- left_join(ape_df,
          gene_names,
          by = "Gene") %>% 
  distinct(Gene, .keep_all = TRUE)
```


```{r}
write_tsv(as.data.frame(ape_df),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/CRB_d35vsd0.tsv")
```

## Arrange DE genes according to their adjusted p-value

```{r}
subset(ape_df, padj < 0.05) -> sig_genes_d35_vs_d0
write_tsv(as.data.frame(sig_genes_d35_vs_d0),"C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/sig_genes_CRB_d35vsd0.tsv")
```

## BARPLOTS FROM ENRICHMENT FILES 

### UPREGULATION

#### BioPlanet enrichr

```{r}
# First we need to install and call the library readxl in order to import the file downloaded from ENRICHR
library(readxl)
# Now we import it putting the path where they are located in your computer
BioPlanet <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/UPREGULATION/BioPlanet_2019_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(BioPlanet$`Adjusted P-value`) -> BioPlanet$`Adjusted P-value`
as.numeric(BioPlanet$`P-value`) -> BioPlanet$`P-value`
# We select only the columns we are interested on
BioPlanet_FDR <- BioPlanet[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
BioPlanet_FDR_top10 <- BioPlanet_FDR[c(1:10),]
#And we change the name of the columns
colnames(BioPlanet_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#To make the plot, we need the function ggplot from the tidyverse library
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is grey
BioPlanet_plot <- ggplot(BioPlanet_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#999999") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 BioPlanet pathway") +
    ylab("-log10(pval)")
BioPlanet_plot <- BioPlanet_plot + theme(text = element_text(size = 5))
BioPlanet_plot
```


#### KEGG enrichr

```{r}
# First we need to install and call the library readxl in order to import the file from the computer
library(readxl)
# Now we import it putting the path where they are located in your computer
KEGG <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/UPREGULATION/KEGG_2021_Human_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(KEGG$`Adjusted P-value`) -> KEGG$`Adjusted P-value`
as.numeric(KEGG$`P-value`) -> KEGG$`P-value`
# We select only the columns we are interested on
KEGG_FDR <- KEGG[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
KEGG_FDR_top10 <- KEGG_FDR[c(1:10),]
#And we change the name of the columns
colnames(KEGG_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is brown
KEGG_plot <- ggplot(KEGG_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="brown3") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 KEGG pathway") +
    ylab("-log10(pval)")
KEGG_plot <- KEGG_plot + theme(text = element_text(size = 5))
KEGG_plot
```

#### GO CELLULAR COMPONENT Enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
GO_Cellular_Component <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/UPREGULATION/GO_Cellular_Component_2023_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(GO_Cellular_Component$`Adjusted P-value`) -> GO_Cellular_Component$`Adjusted P-value`
as.numeric(GO_Cellular_Component$`P-value`) -> GO_Cellular_Component$`P-value`
# We select only the columns we are interested on
GO_Cellular_Component_FDR <- GO_Cellular_Component[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
GO_Cellular_Component_FDR_top10 <- GO_Cellular_Component_FDR[c(1:10),]
#And we change the name of the columns
colnames(GO_Cellular_Component_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is yellow
GO_Cellular_Component_plot <- ggplot(GO_Cellular_Component_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#E69F00") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 GO Celluar Component") +
    ylab("-log10(pval)")
GO_Cellular_Component_plot <- GO_Cellular_Component_plot + theme(text = element_text(size = 5))
GO_Cellular_Component_plot
```

### DOWNREGULATION

#### BioPlanet enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
BioPlanet <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/DOWNREGULATION/BioPlanet_2019_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(BioPlanet$`Adjusted P-value`) -> BioPlanet$`Adjusted P-value`
as.numeric(BioPlanet$`P-value`) -> BioPlanet$`P-value`
# We confirm that they are numeric class
class(BioPlanet$Adjusted.P.value) 
# We select only the columns we are interested on
BioPlanet_FDR <- BioPlanet[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
BioPlanet_FDR_top10 <- BioPlanet_FDR[c(1:10),]
#And we change the name of the columns
colnames(BioPlanet_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is grey
BioPlanet_plot <- ggplot(BioPlanet_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#999999") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 BioPlanet pathway") +
    ylab("-log10(pval)")
BioPlanet_plot <- BioPlanet_plot + theme(text = element_text(size = 5))
BioPlanet_plot
```


#### KEGG enrichr

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
KEGG <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/DOWNREGULATION/KEGG_2021_Human_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(KEGG$`Adjusted P-value`) -> KEGG$`Adjusted P-value`
as.numeric(KEGG$`P-value`) -> KEGG$`P-value`
# We select only the columns we are interested on
KEGG_FDR <- KEGG[,c(1,3,4,9)]
# And now only the first 10 rows/pathways
KEGG_FDR_top10 <- KEGG_FDR[c(1:10),]
#And we change the name of the columns
colnames(KEGG_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
#And now we make the plot using -log10 pval for the representation of the top10 enriched pathways. The number in the fill part represent a color, in this case is brown
KEGG_plot <- ggplot(KEGG_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="brown3") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 KEGG pathway") +
    ylab("-log10(pval)")
KEGG_plot <- KEGG_plot + theme(text = element_text(size = 5))
KEGG_plot
```

#### GO CELLULAR COMPONENT

```{r}
library(readxl)
# Now we import it putting the path where they are located in your computer
GO_Cellular_Component <- read_delim("C:/Users/HR Sergio/Desktop/TFM BIOINFO UOC/BIOINFO_MASTER_SH/d35vsd0/ENRICHR/DOWNREGULATION/GO_Cellular_Component_2023_table.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
#Now we convert all the numbers in numeric values to avoid that R recognizes them as characters
as.numeric(GO_Cellular_Component$`Adjusted P-value`) -> GO_Cellular_Component$`Adjusted P-value`
as.numeric(GO_Cellular_Component$`P-value`) -> GO_Cellular_Component$`P-value`
# We select only the columns we are interested on
GO_Cellular_Component_FDR <- GO_Cellular_Component[,c(1,3,4,9)]
# And now only the first 5 rows/pathways
GO_Cellular_Component_FDR_top10 <- GO_Cellular_Component_FDR[c(1:10),]
#And we change the name of the columns
colnames(GO_Cellular_Component_FDR_top10) <- c("Term", "pval", "FDR", "Genes")
library(tidyverse)
#And now we make the plot using -log10 pval for the representation of the top5 entiched pathways. The number in the fill part represent a color, in this case is yellow
GO_Cellular_Component_plot <- ggplot(GO_Cellular_Component_FDR_top10, aes(x=reorder(Term, -log10(pval)), y=-log10(pval))) +
    geom_bar(stat="identity", alpha=.6, width=.8, fill="#E69F00") +
    coord_flip() +
    theme_classic() +
    xlab("Top 10 GO Cellular components") +
    ylab("-log10(pval)")
GO_Cellular_Component_plot <- GO_Cellular_Component_plot + theme(text = element_text(size = 5))
GO_Cellular_Component_plot
```